Working title: Mirkovi\'c--Vybornov fusion in Beilinson--Drinfeld Grassmannian

### 2020-12-26 main.tex
Added proof of step 1

>>>>

    Proof of Step 1: Let $\mu_1 = (\mu_{1,1}, \mu_{1,2}, ..., \mu_{1,n})$, $\mu_2 = (\mu_{2,1}, ..., \mu_{2,n})$, and $\mu = (\mu^{(1)}, \mu^{(2)}, ..., \mu^{(n)})$. Consider the matrix 
\[
\sbox0{$\begin{matrix}1&2&3\\0&1&1\\0&0&1\end{matrix}$}
A = \left[
\begin{array}{c|c|c|c|c}
    \vphantom{\usebox{0}}\makebox[\wd0]{\large $C_1$}& \begin{matrix} \\ \\ a_{12}^1 & ... & a_{12}^{\mu^{(2)}} \end{matrix} & \makebox[\wd0]{\cdots} & \makebox[\wd0]{\cdots} &  \begin{matrix} \\ \\ a_{1n}^1 & ... & a_{1n}^{\mu^{(n)}} \end{matrix} \\ \hline
     & \vphantom{\usebox{0}}\makebox[\wd0]{\large $C_2$} & \begin{matrix} \\ \\ a_{23}^1 & ... & a_{23}^{\mu^{(3)}}  \end{matrix} & \makebox[\wd0]{\cdots} & \makebox[\wd0]{\vdots} \\ \hline
     & & \vphantom{\usebox{0}}\makebox[\wd0]{\ddots} & \vphantom{\usebox{0}}\makebox[\wd0]{\ddots} & \makebox[\wd0]{\vdots} \\ \hline
     & & & C_{n-1} & \begin{matrix} \\ \\ a_{n-1,n}^1 & ... & a_{n-1,n}^{\mu^{(n)}} \end{matrix} \\ \hline
     & & & & \vphantom{\usebox{0}}\makebox[\wd0]{$C_n$}
\end{array}
\right]
\]
where $C_i$ is the $\mu^{(i)} \times \mu^{(i)}$ companion matrix of $t^{\mu_{1,i}}(t-s)^{\mu_{2,i}}$. We send this matrix to the matrix 
\[
\begin{bmatrix}
    t^{\mu_{1,1}}(t-s)^{\mu_{2,1}} \\
    -\sum_{k=1}^{\mu^{(2)}} a_{12}^k t^{k-1} & t^{\mu_{1,2}}(t-s)^{\mu_{2,2}} \\
    \vdots & \ddots & \ddots \\
    -\sum_{k=1}^{\mu^{(n)}} a_{1n}^k t^{k-1} & \cdots & -\sum_{k=1}^{\mu^{(n)}} a_{n-1,n}^k t^{k-1} & t^{\mu_{1,n}} (t-s)^{\mu_{2,n}}
\end{bmatrix}
\]
\[
= \begin{bmatrix}
    1 \\
    p_{1,2}(t) & 1 \\
    \vdots & \ddots & \ddots \\
    p_{1,n}(t) & \cdots & p_{n-1,n}(t) & 1
\end{bmatrix}
\begin{bmatrix}
    t^{\mu_{1,1}}(t-s)^{\mu_{2,1}} \\
     & \ddots \\
     & & t^{\mu_{1,n}} (t-s)^{\mu_{2,n}}
\end{bmatrix}
\]
where 
\[p_{i,j}(t) = \frac{-\sum_{k=1}^{\mu^{(j)}} a_{i,j}^k t^{k-1}} {t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}}\]
As $\mu_1$ and $\mu_2$ are dominant, we have $p_{i,j}(t) \rightarrow 0$ as $t \rightarrow \infty$ so this matrix is indeed in $G_1[t^{-1},(t-s)^{-1}]t^{\mu_1}(t-s)^{\mu_2}$.
